Digital History in Finland, 1488-1828

### 2016-07-01 inst/examples/manuscript-krakow.Rmd
ok

OK, see lists for
  * [Frenckell Johan Christopher II](output.tables/subjecttopicsFrenckell,_Johan_Christopher_II.tab)
  * [Frenckell Johan Christopher I](output.tables/Frenckell,_Johan_Christopher_I.tab)
  * [Hansson Peter](output.tables/Hansson,_Peter.tab)
  * [Londicer Georg Wilhelm](output.tables/Londicer,_Georg_Wilhelm.tab)
  * [Wall Johan Larsson](output.tables/Wall,_Johan_Larsson.tab)

@@

for (pn in names(x)) {
  fnam <- gsub(" ", "_", pn)
  write_xtable(x[[pn]], file = paste(output.folder, "subjecttopics", fnam, ".tab", sep = ""))
}
```

>>>>

OK, see lists for

  * [Frenckell Johan Christopher II](output.tables/subjecttopicsFrenckell_Johan_Christopher_II.tab)
  * [Frenckell Johan Christopher I](output.tables/Frenckell_Johan_Christopher_I.tab)
  * [Hansson Peter](output.tables/Hansson_Peter.tab)
  * [Londicer Georg Wilhelm](output.tables/Londicer_Georg_Wilhelm.tab)
  * [Wall Johan Larsson](output.tables/Wall_Johan_Larsson.tab)

@@

for (pn in names(x)) {
  fnam <- gsub(",", "", gsub(" ", "_", pn))
  write_xtable(x[[pn]], file = paste(output.folder, "subjecttopics", fnam, ".tab", sep = ""))
}
```
